Code Book
=========

This Codebook is automatically  generated as part of the process for generating the clean tidy dataset.

## Variable list and descriptions


Variable name    | Description
-----------------|------------
subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity         | Activity name
featDomain       | Feature: Time domain signal or frequency domain signal (Time or Freq)
featInstrument   | Feature: Measuring instrument (Accelerometer or Gyroscope)
featAcceleration | Feature: Acceleration signal (Body or Gravity)
featVariable     | Feature: Variable (Mean or SD)
featJerk         | Feature: Jerk signal
featMagnitude    | Feature: Magnitude of the signals calculated using the Euclidean norm
featAxis         | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featCount        | Feature: Count of data points used to compute `average`
featAverage      | Feature: Average of each variable for each activity and each subject

## Dataset structure

```{r}
library(data.table)

pathIn <- file.path("UCI/UCI HAR Dataset/")
tidy <- data.table(read.table(file.path(pathIn, "tidyset.txt"), header = TRUE))

setkey(tidy, subject, activity, featDomain, featAcceleration, featInstrument, 
       featJerk, featMagnitude, featVariable, featAxis)

str(tidy)
```


## Show some of the dataset entries

```{r}
head(tidy, 5)
```

## Summary of variables
```{r}
summary(tidy)
```

