Code Book
=========

This Codebook is automatically  generated as part of the process for generating the clean tidy dataset. The run_analysis.R script uses the $codebook.Rmd$ template to compile a codebook.md file.

## Variable list and descriptions


Variable name    | Description
-----------------|------------
subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity         | Activity name
Domain           | Feature: Time domain signal or frequency domain signal (Time or Freq)
Instrument       | Feature: Measuring instrument (Accelerometer or Gyroscope)
Acceleration     | Feature: Acceleration signal (Body or Gravity)
Variable         | Feature: Variable (Mean or SD)
Jerk             | Feature: Jerk signal
Magnitude        | Feature: Magnitude of the signals calculated using the Euclidean norm
Axis             | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
count            | Feature: Count of data points used to compute `average`
average          | Feature: Average of each variable for each activity and each subject

## Dataset structure

This codebook expects to have the tidy dataset in the output directory
created by run_analsys.R script. It is then imperative to run the run_analysis.R script before opening the coodbook.md file, or it will not work.
```{r}
library(data.table)

pathIn <- file.path("UCI/UCI HAR Dataset/")
tidy <- data.table(read.table(file.path(pathIn, "tidyset.txt"), header = TRUE))

setkey(tidy, subject, activity, Domain, Acceleration, Instrument, 
       Jerk, Magnitude, Variable, Axis)

str(tidy)
```


## Show the first five dataset entries

```{r}
head(tidy, 5)
```

## Summary of variables
```{r}
summary(tidy)
```

